\Huge\textbf{Mbrane}\linebreak\linebreak\linebreak \Large\textbf{Final Report}\linebreak\linebreak \linebreak\linebreak \includegraphics[scale=0.1]{feup-logo.png}\linebreak\linebreak \linebreak\linebreak \Large{Logic Programing}\linebreak

### 2019-11-17 docs/report_latex/template.tex
commenting

% TODO
\section*{Summary}
Resumo do trabalho (aprox. 250 palavras) descrevendo sucintamente o problema abordado, objetivos, metodologia usada na sua resolução, principais resultados e conclusões).

\paragraph{} 
The goal of this project was to program a board game using the prolog language. In our case the game in question is Mbrane, a 
game created by DukeZhou based on Sudoku and strategy games like chess. Section 2 clarifies all the aspects of this game.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
% TODO complete
\section{Introduction}
\paragraph{}
This project was developed during the Logic Programing Course in the context of the third the Integrated Masters in Informatics 
and Computing Engineering. The goal is to implement in Prolog a board game, in this case \textit{Mbrane}.

@@

% TODO complete
\subsection{Game state representation} 
Although the user can only be able to see one board at a time, in a any phase of the game, there are actually three
boards represented in the game’s data structures. There’s a board predicate that represents the game board itself, a
list of 9 lists each representing a line of the board. This is the board used to print the state of the game. There’s 
also a \textbf{board\_blocks} predicate. This predicate is also a list of 9 lists, each one representing a 3 by 3 block of the 
board, this is used to facilitate calculations involving power in each block and influence in adjacent blocks caused 
by the placement of a number in the edge of a block. Finally we have a \textbf{board\_influence} list that stores the values of 
power (and spread influence) in each block of the board.  When a player adds a number to cell, all the boards are 
updated accordingly.

% TODO complete
\subsection{Board viewing} 
Before each move, the board is displayed on the screen. To display the board we use the predicate \textit{display\_game(+Board, +Player1, +Player2)}. This predicate first displays the players' names and then uses \textit{display\_board(+Board)} to display the board itself. 
The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.

% TODO complete
\subsection{List valid plays} 
As per requested, we developed a predicate that returns a list of all possible moves. This predicate is \textit{valid\_moves(+Board, -R)}. The first argument of the predicate is a list with the board of lines and board of blocks.
This predicate works by first finding a list of all empty cells with \textit{check\_all(+Board, -List),}. Then it tests all possible values in those cells with \textit{test_all(+List, +Board, +Result)}.

% TODO complete
\subsection{Play execution} 
Each player can make a move per turn \textit{player\_turn(+Board, +Player, -NewBoard)}. In this turn predicate, the program asks the player what he wants to play with \textit{get_move(-X, -Y, -V)} then the program tries that move with \textit{move(+Move, +Board, -NewBoard)}.
If the move is invalid the program repeats the previous action, otherwise, it returns a new board with the new piece.

@@

% TODO complete
\subsection{Game finalization} 
Verificação do fim do jogo, com identificação do vencedor. O predicado deve chamar-se \textit{game\_over(+Board, -Winner)}.

\paragraph{}
The game is in the final state if no more numbers can be placed on the board. When this happens the game enters the 
\textbf{Resolution Phase} and proceds to make the calculartions mentioned in \textbf{Section 2}. Then the winner (if it exists) is
announced.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
% TODO complete
\section{Conclusions}
Que conclui deste projecto? Como poderia melhorar o trabalho desenvolvido?

>>>>

\section*{Summary}

The goal of this project was to program a board game using the prolog language. In our case the game in question is Mbrane, a 
game created by DukeZhou based on Sudoku and strategy games like chess. Section 2 clarifies all the aspects of this game.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\paragraph{}
This project was developed during the Logic Programing Course in the context of the third the Integrated Masters in Informatics 
and Computing Engineering. The goal is to implement in Prolog a board game, in this case \textit{Mbrane}.

@@

\subsection{Game state representation} 
Although the user can only be able to see one board at a time, in a any phase of the game, there are actually three
boards represented in the game’s data structures. There’s a board predicate that represents the game board itself, a
list of 9 lists each representing a line of the board. This is the board used to print the state of the game. There’s 
also a \textbf{board\_blocks} predicate. This predicate is also a list of 9 lists, each one representing a 3 by 3 block of the 
board, this is used to facilitate calculations involving power in each block and influence in adjacent blocks caused 
by the placement of a number in the edge of a block. Finally we have a \textbf{board\_influence} list that stores the values of 
power (and spread influence) in each block of the board.  When a player adds a number to cell, all the boards are 
updated accordingly.

\subsection{Board viewing} 
Before each move, the board is displayed on the screen. To display the board we use the predicate \textit{display\_game(+Board, +Player1, +Player2)}. This predicate first displays the players' names and then uses \textit{display\_board(+Board)} to display the board itself. 
The board is displayed line by line with a series of dividers. Although for game logic the values of the board can be positive or negative, the board is printed with only positive numbers.

\subsection{List valid plays} 
As per requested, we developed a predicate that returns a list of all possible moves. This predicate is \textit{valid\_moves(+Board, -R)}. The first argument of the predicate is a list with the board of lines and board of blocks.
This predicate works by first finding a list of all empty cells with \textit{check\_all(+Board, -List),}. Then it tests all possible values in those cells with \textit{test_all(+List, +Board, +Result)}.

\subsection{Play execution} 
Each player can make a move per turn \textit{player\_turn(+Board, +Player, -NewBoard)}. In this turn predicate, the program asks the player what he wants to play with \textit{get_move(-X, -Y, -V)} then the program tries that move with \textit{move(+Move, +Board, -NewBoard)}.
If the move is invalid the program repeats the previous action, otherwise, it returns a new board with the new piece.

@@

\subsection{Game finalization} 
For the end of game we need to verify if there are any possible moves left. This is done by predicate \textit{game\_over(+Board, -Winner)}. If there are any moves left, it fails and the game continues.
Otherwise it will find out who won the game. This is done by verifying which player controls the most blocks in the predicate \textit{get\_winner(+Board, -Winner)}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\pagebreak
% TODO complete
\section{Conclusions}
With this work we have developed our way of thinking in a new way. Although Prolog can be compared to other programming languages, it is unique in the way it works.
The biggest problem we found was trying to make use of dynamic predicates to create a sort of global board. After testing a lot we decided to give up on the idea.
In terms of the game mechanics, there are a lot of verifications
